master thesis

### 2018-03-05 Paper - Latex/Paper - Skizze - v2.tex
Paper - Methods:remove countings; - Results - Unknown leaf nodes

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{Countings}
      \begin{center}
        \begin{tabular}{ | l | l | }
          \hline
          Name & Number of \\
          \hline \hline
          Eukaryota & 241 974 internal nodes, \\
          & 2 293 463 leaf nodes \\ \hline
          % Chloroplastida has 43486 internal nodes and 412434 leaf_nodes
          % Metazoa has 179944 internal nodes and 1491012 leaf_nodes
          % Nematoda has 3437 internal nodes and 30127 leaf_nodes
          % Vertebrata has 30466 internal nodes and 88415 leaf_nodes
          % Tetrapoda has 21870 internal nodes and 47540 leaf_nodes
          % Mammalia has 4727 internal nodes and 8615 leaf_nodes
          % Primates has 492 internal nodes and 686 leaf_nodes
          % Hominidae has 12 internal nodes and 14 leaf_nodes
          % Fungi has 9534 internal nodes and 314571 leaf_nodes
          interactions & 5 346 414 \\ \hline
          freeliving species & 51 337 (distinct) \\ \hline
          parasite species &  47 332 (distinct) \\ \hline
          $\rightarrow$ unknown nodes & ??? \\ \hline
          unused possible species & 57 352 (source), \\
          & 809 993 (target) \\
          % number of freelivings: 489179
          % number of freelivings: 42657 (distinct)
          % number of parasites: 3353580
          % number of parasites: 44260 (distinct)
          % number of SAME_AS: 86198
          % number of SAME_AS: 16710 (distinct)
          \hline
          Nr of Children $== 1$ & 55 700 \\
          & 51 744 (height $=2$) \\
          & 3 956 (height $>2$) \\ \hline
        \end{tabular}
      \end{center}
      \todo{tree, subtrees? figure dazu?} \\
      $\frac{100}{2293463 * (51337 + 47332)} \approx 4.3$ $\rightarrow$ only 4.3\% of leaf nodes are 
        filled with information

      \#interactions zu \#Parasiten und \#Freilebend $\rightarrow$ Wieviel gibt GloBI her? (dazu noch 
        \#unused possible species, wieviele Parasiten ohne ott haben wir gefunden?)
      \#Parasiten und \#Freilebend und \#Blattknoten $\rightarrow$ Wieviele unbekannte Knoten haben wir?
      \#Interne Knoten und \#Blattknoten $\rightarrow$ Wie stark ist die Multifurkation?

@@

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \section{Multifurcation}\label{sec:ResultsMultifurcation}
      One property of the tree is its ridge of multifurcation. A complete phylogenetic tree would be 
        binary, but since we only work with a synthesis tree, this tree is multifurcated. \\
      For a first overview we collected for every node its number of children (degree $-1$), and plotted
        this in an histogram, see figure \ref{fig:childrenOfNodes}. The multifurcation affects only the
        internal nodes. We collected the number of children $-2$ of every node (a node with two children 
        is binary). 
      \begin{wrapfigure}{r}{0.6\textwidth}
        \begin{center}
          \includegraphics[trim = 0mm 0mm 30mm 0mm, clip, width=0.58\textwidth]{Figures/multifurc.pdf}
        \end{center}
        \caption{Histogram about the multifurcation of the internal nodes of the synthesis tree. \\ 
          light blue: binary; dark blue: multifunction}
        \label{fig:childrenOfNodes}
      \end{wrapfigure}
      That means it discribes the number of nodes which we have lost from the real (binary) 
      phylogenetic tree. \\
      As you can see, we are very far from a binary tree.

      %---------------------------------------------------------------------------------------------------
      \subsubsection{Data artifacts}
      At this point we also found out that there are some nodes with only one child node (55700 nodes). \\
      These are both, the most nodes are right in front of a leaf, as well as some nodes are deep in the 
        tree (3956 with height $>2$). They are probably a result from the fact that taxonomic information 
        has been incorporated into a phylogeny. \\

      Some examples:
      \begin{itemize}
        \item Nephroselmidophyceae: (class) \\
          https://tree.opentreeoflife.org/opentree/argus/ottol@1038762
        \item Phrynocrinidae: (family) \\
          https://tree.opentreeoflife.org/opentree/argus/ottol@3647979
        \item Elaeocarpus sylvestris: \\
          https://tree.opentreeoflife.org/opentree/argus/opentree9.1@ott166969
      \end{itemize}

@@

        \begin{table}
          \begin{center}
            \begin{tabular}{ |l|r|r|r|r| }
              \hline
              Model / Taxa & Kingdom & Phylum & Class & Order \\
              \hline \hline
              multifurc $\sim$ taxa & 7774454 & 7435700 & 7337241 & 7076068 \\
              \hline
              multifurc $\sim$ taxa + depth & 7752303 & 7431609 & 7334754 & 7027578 \\
              multifurc $\sim$ taxa + max.height & 7730196 & 7375889 & 7275856 & 7005424 \\
              multifurc $\sim$ taxa + min.height & 7472500 & 7233486 & 7144686 & \cellcolor{green!50}6890703 \\
              multifurc $\sim$ taxa + mean.height & 7304402 & 7128318 & 7055313 & \cellcolor{green!50}6815271 \\
              \hline
              multifurc $\sim$ taxa * depth & 7714881 & 7335396 & 7250759 & \\
              multifurc $\sim$ taxa * max.height & 7692980 & 7311241 & 7187504 & \\
              multifurc $\sim$ taxa * min.height & 7442387 & 7177002 & 7094933 & \\
              multifurc $\sim$ taxa * mean.height & 7247309 & 7020258 & \cellcolor{green!50}6965794 & \\
              \hline
            \end{tabular} 
          \end{center}
          \caption{Residuals...}
          \label{table:...} 
        \end{table}
        * Residuals: Fehler - wieviele Werte sind nicht gut modelliert. (umso kleiner umso besser - grün) \\

@@

        Because of the difference in the complexity of the models, we compared their BICs:
        \begin{table}
          \begin{center}
            \begin{tabular}{ |l|r|r|r|r| }
              \hline
              Model / Taxa & Kingdom & Phylum & Class & Order \\
              \hline \hline
              multifurc $\sim$ taxa & 8273333 & 7937828 & 7842157 & 7644249\\
              \hline
              multifurc $\sim$ taxa + depth & 8273318 & 7934322 & 7839364 & \\
              multifurc $\sim$ taxa + max.height & 7993515 & 7749121 & 7661817 & \\
              multifurc $\sim$ taxa + min.height & 8251211 & 7875521  & 7778327 & \\
              multifurc $\sim$ taxa + mean.height & 7825417 & 7644249 &  \cellcolor{green!50}7572474 & \\
              \hline
              multifurc $\sim$ taxa * depth & 8235932 & 7836755 & 7757688 & \\
              multifurc $\sim$ taxa * max.height & 7963438 & 7693555 & 7614820 & \\
              multifurc $\sim$ taxa * min.height & 8214030 & 7808940 & 7690618 & \\
              multifurc $\sim$ taxa * mean.height & 7768360 & \cellcolor{green!50}7536296 & \cellcolor{green!50}7484953 & \\
              \hline
            \end{tabular} 
          \end{center}
          \caption{BIC...}
          \label{table:...} 
        \end{table}

@@

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Results of simulation}

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{Influence of different parameters}

    \begin{figure}
      \caption{Influence of unknown data to prediction}
      \centering
      \includegraphics[width=0.9\textwidth]{Figures/simulation_evaluation_1.png}
    \end{figure}

>>>>

@@

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \section{Multifurcation}\label{sec:ResultsMultifurcation}
      One property of the tree is its ridge of multifurcation. A complete phylogenetic tree would be 
        binary, which means the number of leaf nodes is closely to the number of internal nodes. But 
        since we only work with a synthesis tree, this tree is multifurcated: we have 241 974 internal 
        nodes and 2 293 463 leaf nodes. \\
      For a first overview we collected for every node its number of children (degree $-1$), and plotted
        this in an histogram, see figure \ref{fig:childrenOfNodes}. The multifurcation affects only the
        internal nodes. We collected the number of children $-2$ of every node (a node with two children 
        is binary). 
      \begin{wrapfigure}{r}{0.6\textwidth}
        \begin{center}
          \includegraphics[trim = 0mm 0mm 30mm 0mm, clip, width=0.58\textwidth]{Figures/multifurc.pdf}
        \end{center}
        \caption{Histogram about the multifurcation of the internal nodes of the synthesis tree. \\ 
          light blue: binary; dark blue: multifunction}
        \label{fig:childrenOfNodes}
      \end{wrapfigure}
      That means it discribes the number of nodes which we have lost from the real (binary) 
      phylogenetic tree. \\
      As you can see, we are very far from a binary tree.

      %---------------------------------------------------------------------------------------------------
      \subsubsection{Data artifacts}
      At this point we also found out that there are some nodes with only one child node (55700 nodes). \\
      These are both, the most nodes are right in front of a leaf, as well as some nodes are deep in the 
        tree (3956 with height $>2$). They are probably a result from the fact that taxonomic information 
        has been incorporated into a phylogeny. \\
      Some examples:
      \begin{itemize}
        \item Nephroselmidophyceae: (class) \\
          https://tree.opentreeoflife.org/opentree/argus/ottol@1038762
        \item Phrynocrinidae: (family) \\
          https://tree.opentreeoflife.org/opentree/argus/ottol@3647979
        \item Elaeocarpus sylvestris: \\
          https://tree.opentreeoflife.org/opentree/argus/opentree9.1@ott166969
      \end{itemize}

@@

        \begin{table}[h]
          \begin{center}
            \begin{tabular}{ |l|r|r|r|r| }
              \hline
              Model / Taxa & Kingdom & Phylum & Class & Order \\
              \hline \hline
              multifurc $\sim$ taxa & 7774454 & 7435700 & 7337241 & 7076068 \\
              \hline
              multifurc $\sim$ taxa + depth & 7752303 & 7431609 & 7334754 & 7027578 \\
              multifurc $\sim$ taxa + max.height & 7730196 & 7375889 & 7275856 & 7005424 \\
              multifurc $\sim$ taxa + min.height & 7472500 & 7233486 & 7144686 & \cellcolor{green!50}6890703 \\
              multifurc $\sim$ taxa + mean.height & 7304402 & 7128318 & 7055313 & \cellcolor{green!50}6815271 \\
              \hline
              multifurc $\sim$ taxa * depth & 7714881 & 7335396 & 7250759 & \\
              multifurc $\sim$ taxa * max.height & 7692980 & 7311241 & 7187504 & \\
              multifurc $\sim$ taxa * min.height & 7442387 & 7177002 & 7094933 & \\
              multifurc $\sim$ taxa * mean.height & 7247309 & 7020258 & \cellcolor{green!50}6965794 & \\
              \hline
            \end{tabular} 
          \end{center}
          \caption{Residuals...}
          \label{table:...} 
        \end{table}
        * Residuals: Fehler - wieviele Werte sind nicht gut modelliert. (umso kleiner umso besser - grün) \\

@@

        Because of the difference in the complexity of the models, we compared their BICs:
        \begin{table}[h]
          \begin{center}
            \begin{tabular}{ |l|r|r|r|r| }
              \hline
              Model / Taxa & Kingdom & Phylum & Class & Order \\
              \hline \hline
              multifurc $\sim$ taxa & 8273333 & 7937828 & 7842157 & 7644249\\
              \hline
              multifurc $\sim$ taxa + depth & 8273318 & 7934322 & 7839364 & \cellcolor{green!50}7539999 \\
              multifurc $\sim$ taxa + max.height & 7993515 & 7749121 & 7661817 & \cellcolor{green!50}7416211 \\
              multifurc $\sim$ taxa + min.height & 8251211 & 7875521  & 7778327 & \cellcolor{green!50}7516883 \\
              multifurc $\sim$ taxa + mean.height & 7825417 & 7644249 & \cellcolor{green!50}7572474 & \cellcolor{green!50}7340741 \\
              \hline
              multifurc $\sim$ taxa * depth & 8235932 & 7836755 & 7757688 & \cellcolor{green!50}7383808 \\
              multifurc $\sim$ taxa * max.height & 7963438 & 7693555 & 7614820 & \\
              multifurc $\sim$ taxa * min.height & 8214030 & 7808940 & 7690618 & \\
              multifurc $\sim$ taxa * mean.height & 7768360 & \cellcolor{green!50}7536296 & \cellcolor{green!50}7484953 & \\
              \hline
            \end{tabular} 
          \end{center}
          \caption{BIC...}
          \label{table:...} 
        \end{table}

  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  %---------------------------------------------------------------------------------------------------
  \section{Unknown leaf nodes}
    Next to the problem of the multifurcation of the tree is the less of data we have for the species.
      For the ancestral state reconstruction, we need information in the leaf nodes. \\
    The eukaryotic synthesis tree has 293 463 leaf nodes. The GloBI database has 5 346 414 interactions 
      (at this timepoint). Out of this data we got 51 337 distinct free-living species and 47 332 
      distinct parasite species $\rightarrow$ unknown nodes 2194794 ($\approx 95.7\%$). \\
    With this only $\approx 4.3\%$ information in our leaf nodes are

    \todo{einbauen?:} \\
    unused possible species  57 352 (source), \\
    809 993 (target) \\

    \#interactions zu \#Parasiten und \#Freilebend $\rightarrow$ Wieviel gibt GloBI her? (dazu noch 
      \#unused possible species, wieviele Parasiten ohne ott haben wir gefunden?)

    %---------------------------------------------------------------------------------------------------
    %---------------------------------------------------------------------------------------------------
    \subsection{Results of simulation / Influence of different parameters}

    \begin{figure}
      \caption{Influence of unknown data to prediction}
      \centering
      \includegraphics[trim = 0mm 0mm 0mm 50mm, clip,width=0.9\textwidth]{Figures/simulation_evaluation_1.png}
    \end{figure}

@@
